Local Adaptive Optimization of Time Step

### 2013-10-06 report/presentation_content.tex
Presentation of experimental plan done

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

@@

\section{The project in short}
\begin{frame}{Short introduction to the project}
    \begin{itemize}
		\item Simulations of materials
		\item Huge amount of computations for large materials
        \item Reduce avg. number of calculations/time
	\end{itemize}
\end{frame}

\begin{frame}{Illustration of motivation}
    \begin{figure}
        \center
        \includegraphics[width=\linewidth,keepaspectratio]{../images/spring_motivation.png}
        \caption{Simulations of mass spring particle system}
        \label{fig:motivation}
    \end{figure}
\end{frame}

\section{Experimental plan}
\begin{frame}{Overview of experiments}
    \begin{itemize}
        \item 1D experiments (simple)
        \item 2D experiments (more complex)
        \item Apply methods for uniform meshes 
        \item Apply methods for multi-scale meshes
        \item Compare method with regular timestepping
    \end{itemize}
\end{frame}

\subsection{1D experiments}
\begin{frame}{1D experiments}
    \begin{itemize}
        \item Application: Mass spring particle system
        \item Hook's law
        \item Simplicity for ease of development
    \end{itemize}
\end{frame}

\subsection{2D experiments}
\begin{frame}{2D experiments}
    \begin{itemize}
        \item Extend 1D scheme
        \item Application: Hyperelastic materials
        \item Stress and strain
    \end{itemize}
\end{frame}

\subsection{Performance experiments}
\begin{frame}{Performance experiments}
    \begin{itemize}
        \item Total simulation time
    \end{itemize}
\end{frame}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\newcommand{\itemv}[1]{\item{#1}}

@@

\section{The project in short}
\begin{frame}{Short introduction to the project}
    \pause\begin{itemize}[<+->]
		\itemv Materials
        \begin{itemize}
            \itemv In real life: Continuous
            \itemv In simulations: Discrete representations using
                particles/grids
        \end{itemize}
		\itemv Large/detailed materials = huge amount of particles/vertices
        \itemv Varying grid size/scale
        \itemv Simulation of time
        \itemv Reduce avg. number of calculations/time
	\end{itemize}
\end{frame}

\begin{frame}{Illustration of motivation}
    \begin{figure}
        \center
        \includegraphics[width=\linewidth,height=6cm]{../images/spring_motivation.png}
        \caption{Simulations of mass spring particle system}
        \label{fig:motivation}
    \end{figure}
\end{frame}

\section{Experimental plan}
\begin{frame}{Overview of experiments}
    \pause\begin{itemize}[<+->]
        \itemv 1D experiments (simple)
        \itemv 2D experiments (more complex)
        \itemv Use experiments to develop schemes
        \itemv Apply methods for uniform meshes 
        \itemv Apply methods for multi-scale meshes
        \itemv Compare method with regular timestepping
    \end{itemize}
\end{frame}

\subsection{1D experiments}
\begin{frame}{1D experiments}
    \pause\begin{itemize}[<+->]
        \itemv 1D for simplicity and ease of development
        \itemv Develop a scheme from experimenting
        \itemv Application: Mass spring particle system (clothes)
        \itemv Hook's law
        \itemv Uniform and multi-scale meshes and simulations
    \end{itemize}
\end{frame}

\subsection{2D experiments}
\begin{frame}{2D experiments}
    \pause\begin{itemize}[<+->]
        \itemv Extend 1D scheme to 2D
        \itemv Gain in complexity
        \itemv Application: Hyperelastic materials
        \itemv Stress and strain
        \itemv Uniform and multi-scale meshes and simulations
    \end{itemize}
\end{frame}

\subsection{Performance experiments}
\begin{frame}{Performance experiments}
    \pause\begin{itemize}[<+->]
        \itemv Total simulation time
        \itemv Compare our 2D scheme with regular time stepping
        \itemv Only sequential tests
        \itemv Only in Matlab
    \end{itemize}
\end{frame}
